% Created by Alexander Baker, original repo here: https://github.com/AlexLBaker/LaTeX-Cover-Letter

\documentclass{cover_class}

\begin{document}

% Header
\coverheader{Alexander Logan Baker}{Director of Data Analytics}
\hfill
\coverinfo{alexander.l.baker@outlook.com}{+1 (317) 205-7608}{LinkedIn.com/alexander-baker}{GitHub.com/AlexLBaker}{2050 Ruckle St, Indianapolis, IN 46202}
\vspace{12pt}
\hrule
\vspace{12pt}

% Date
\noindent\textbf{\today}
\vspace{1em}

% Company's information
\noindent{Siemens AG}\\
\noindent{300 New Jersey Avenue Suite 1000,}\\
\noindent{Washington, D.C. 20001}\\

\begin{spacing}{1.4}

\noindent{Dear Hiring Manager,}

\vspace{6pt}

I am thrilled to express my interest in the Financial Data Analyst position at Siemens within the Digital Industries Software division. The remarkable work Siemens has been doing in revolutionizing the digital enterprise aligns seamlessly with my aspirations, and I am excited about the possibility of contributing to your mission.

Siemens' commitment to driving the digital transformation of accounting functions resonates deeply with my passion for leveraging data analytics to bring about meaningful change. The opportunity to collaborate with a team of diverse experts in a fast-growing environment is precisely the kind of challenge I am eager to take on.

Having attained a master's degree with a focus on data science and gained valuable financial analytics experience in a consulting setting, I am well-equipped to contribute to Siemens' vision. My proficiency in leading-edge analytics tools and understanding of programming languages for data science, make me confident in my ability to deliver results that align with Siemens' goals.

Siemens' reputation for fostering innovation, coupled with the emphasis on an intellectually stimulating environment, makes it the perfect platform for me to grow both personally and professionally. I am eager to leverage my skills in driving digital transformation, automating processes, and delivering insights that matter.

Thank you for considering my application. I am excited about the prospect of joining Siemens and making a meaningful impact on your digital journey.

\vspace{6pt}
\noindent{Sincerely,}

\vspace{6pt}
\noindent{Alexander Baker}
\end{spacing}
\end{document}